% --- LaTeX CV Template - S. Venkatraman ---

% Set document class and font size
\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}

% Package imports
\usepackage{setspace, longtable, graphicx, hyphenat, hyperref, fancyhdr, ifthen, everypage, enumitem, amsmath, setspace}

% --- Page layout settings ---

% a4paper: 210 x 297 mm
% Set page margins
\usepackage[left=15mm, right=15mm, bottom=30mm, top=30mm]{geometry}

% Set line spacing
\renewcommand{\baselinestretch}{1.0}

% --- Page formatting ---

% Set link colors
\usepackage[dvipsnames]{xcolor}
\hypersetup{colorlinks=true, linkcolor=RoyalBlue, urlcolor=RoyalBlue}

% Set font to Libertine, including math support
\usepackage{libertine}
\usepackage[libertine]{newtxmath}

% Remove page numbering
%\pagenumbering{gobble}

% 自定义颜色
\usepackage{color} \definecolor{tsukuba}{RGB}{148,73,219} % tsukuba - 筑波的紫色
% OliveGreen
% black
\newcommand{\lefttitle}[1]{\color{black}{\textsc{#1}}}

% --- Document starts here ---

\begin{document}
	
	% Name and date of last update to this document
	\noindent{\Huge{\textsc{Zhijian Lai}}  
		\hfill{\it\footnotesize Updated \today}}
	
	% --- horizontal line ---
	\hrule
	
	% --- Contact information ---
	\vspace{2mm} 
			
	% Set spacing between columns
	\setlength{\tabcolsep}{7pt}
	
	% Set the width of each column
	\begin{longtable}{p{30mm}p{140mm}}
				
		% --- Section: Connect Information ---
		\nohyphens{\lefttitle{Connect Information}}
		& {{Email}: s2130117@s.tsukuba.ac.jp
			
			{Office}: 3E310, 1-1-1 Tennodai, Tsukuba, Ibaraki, 305-8577, Japan
			
			{Homepage}: {\footnotesize\url{https://galvinlai.github.io/}}
		} \\
		& \\
		
		% --- Section: Research Interests ---
		\nohyphens{\lefttitle{Research Interests}}
		& Mathematical Optimization, Riemannian Optimization, Machine Learning, Deep Learning, Quantum Computing \\
		& \\
		
		% --- Section: Education ---
		\lefttitle{Education}
		& \textbf{University of Tsukuba} \hfill Tsukuba, Japan \\
		& Ph.D. of Science in Policy and Planning Sciences \hfill Apr. 2021 -- Mar. 2024 (expected) \\
		& Master of Science in Policy and Planning Sciences \hfill Apr. 2019 -- Mar. 2021\\
		& Supervisor: Prof. \href{https://scholar.google.com/citations?hl=en&user=-iam1HEAAAAJ}{Akiko Yoshise} \\
		& \\
		
		& \textbf{Dongbei University of Finance and Economics} \hfill Dalian, China\\
		& Bachelor of Management \hfill Sep. 2013 – June 2017\\
		& \\
		
		% --- Section: Grants and fellowship ---
		\lefttitle{Grants}
		& Research fellowship of \textit{Support for Pioneering Research Initiated by the Next Generation} (SPRING), Japan Science and Technology Agency \hfill Sep. 2021 -- Present\\
		& \\		
			
		% --- Uncomment the next few lines if you want to include some courses ---
		%& \textbf{Selected coursework}
		%\begin{itemize}[noitemsep,leftmargin=*]
		%\item \textbf{Relevant subject 1}: Course 1, Course 2, Course 3, Course 4
		%\item \textbf{Relevant subject 2}: Course 1, Course 2, Course 3, Course 4
		%\end{itemize} \\
		
		% --- Section: Working Papers ---
		\nohyphens{\lefttitle{Working Papers}} 
		& {CLAP: A Contrastive Learning Structure for App-usage Prediction} \\	
		& Xin Yang, \textbf{Zhijian Lai}, Qian Wu, Maiko Shigeno. \\
		& \\
		
		& {HGCL4REC: Hyperbolic Graph Contrastive Learning for Recommender System} \\
		& Xin Yang, \textbf{Zhijian Lai}, Qian Wu, Maiko Shigeno. \\
		& \\
		
		% --- Section: Publications and Preprints ---			
		\lefttitle{Publications and} 
		& {Completely Positive Factorization by a Riemannian Smoothing Method} \\
		\lefttitle{Preprints} 
		& \textbf{Zhijian Lai}, Akiko Yoshise. \\
		& \textit{Computational Optimization and Applications}, 2022.\\
		& \\
		
		& {Riemannian Interior Point Methods for Constrained Optimization on Manifolds} \\
		& \textbf{Zhijian Lai}, Akiko Yoshise. \\
		& \textit{arxiv.org/abs/2203.09762}, 2023.  (Submitted to JOTA)\\
		& \\		
											
		% --- Section: International Conference Talks --- 
		{\lefttitle{International}} 
		& {ICIAM 2023} \hfill Aug. 2023 \\
		{\lefttitle{Conference Talks}} 
		& \textbf{Zhijian Lai}, Akiko Yoshise. \textit{Riemannian Interior Point Methods for Constrained Optimization on Manifolds}, Tokyo.  \\
		&  \\
		
		& {SIAM OP23} \hfill June 2023 \\
		& \textbf{Zhijian Lai}, Akiko Yoshise. \textit{Interior Point Methods for Nonlinear Optimization on Riemannian Manifolds}, Seattle.  \\
		&  \\
		
		& {International Workshop on Continuous Optimization} \hfill Dec. 2022 \\
		& \textbf{Zhijian Lai}, Akiko Yoshise. \textit{Riemannian Interior Point Methods for Constrained Optimization on Manifolds}, Tokyo (virtual).  \\
		&  \\
		
		& {SIAM OP21} \hfill July 2021 \\
		& \textbf{Zhijian Lai}, Akiko Yoshise. \textit{Completely Positive Factorization via Orthogonality Constrained Problem}, Hong Kong (virtual). \\
		& \\
		
		% --- Section: Domestic Conference Talks --- 
		{\lefttitle{Domestic (Japan)}} 
		& {RAOTA: Gathering of Young Researchers for the Future 2023} \hfill May 2023 \\
		{\lefttitle{Conference Talks}} 
		& \textbf{Zhijian Lai}, Akiko Yoshise. \textit{Riemannian Interior Point Methods for Constrained Optimization on Manifolds}, Tsukuba, Japan. \\
		& \\
		
		\newpage
		
		& {The 2023 spring national conference of Operations Research Society of Japan} \hfill Mar. 2023 \\
		& \textbf{Zhijian Lai}, Akiko Yoshise. \textit{Riemannian Interior Point Methods for Constrained Optimization on Manifolds}, Tokyo, Japan. \\
		& \\
		
		& {The 2022 autumn national conference of Operations Research Society of Japan} \hfill Sep. 2022 \\
		& \textbf{Zhijian Lai}, Akiko Yoshise. \textit{On the Global Convergence of Riemannian Interior Point Method}, Niigata (virtual), Japan. \\
		& \\
				
		& {The Japan Society for Industrial and Applied Mathematics 2022 annual meeting} \hfill Sep. 2022 \\
		& \textbf{Zhijian Lai}, Akiko Yoshise. \textit{On the Global Convergence of Riemannian Interior Point Method}, Sapporo, Japan. \\
		& \\	
			
		& {The 2022 spring national conference of Operations Research Society of Japan} \hfill Mar. 2022 \\
		& \textbf{Zhijian Lai}, Akiko Yoshise. \textit{Superlinear and Quadratic Convergence of Riemannian Interior Point Methods}, Gunma (virtual), Japan. \\
		& \\

		& {Meeting 2021 of Kyoto University Research Institute for Mathematical Sciences} \hfill Aug. 2021 \\
		& \textbf{Zhijian Lai}, Akiko Yoshise. \textit{Application of Smoothing Methods for Completely Positive Matrices via Orthogonality Constrained Problem}, Kyoto (virtual), Japan. \\
		& \\
		
		& {The 2021 spring national conference of Operations Research Society of Japan} \hfill Mar. 2021 \\
		& \textbf{Zhijian Lai}, Akiko Yoshise. \textit{Completely Positive Factorization via Orthogonality Constrained Problem}, Tokyo (virtual), Japan. \\
		& \\

		& {Meeting 2020 of Kyoto University Research Institute for Mathematical Sciences} \hfill Aug. 2020 \\
		& \textbf{Zhijian Lai}, Akiko Yoshise. \textit{A New Approach to the Recognition Problem of Completely Positive Matrices}, Kyoto (virtual), Japan. \\
		& \\

		% --- Section: Poster ---		
		\nohyphens{\lefttitle{Poster}} 
		& {Poster Session of 2022 SPRING Fellowship} \hfill Mar. 2023 \\
		& \textbf{Zhijian Lai}. \textit{Riemannian Interior Point Methods for Manifold Optimization}, Tsukuba, Japan. \\
		& \\

		% --- Section: Research experience ---
		\nohyphens{\lefttitle{Research}} 
		& {Research Assistant, University of Tsukuba} \hfill Apr. 2021 -- Present \\
		\nohyphens{\lefttitle{Experience}}
		& Supervisor: Prof. Akiko Yoshise \\
		& \\
				
		% --- Section: Teaching experience ---	
		\nohyphens{\lefttitle{Teaching}} 
		& {Teaching Assistant, College of Policy and Planning Sciences, University of Tsukuba}  \\
		\nohyphens{\lefttitle{Experience}} 
		& - FH61141: Society and Optimization \hfill Fall 2023 \\
		& - FH35012: Problem Identification and Resolution \hfill Fall 2022 \\
		& - FH61141: Problem Identification and Resolution \hfill Fall 2022 \\
		& - 0AL5100: Supply Chain Management \hfill Fall 2021  \\
		& \\
		
		& {Mathematics Tutoring for Graduate Admission Examination, Graduate School for Policy and Planning Sciences, University of Tsukuba}  \\
		& - Linear Algebra \hfill Aug. 2021 \\
		& - Calculus \hfill Dec. 2019 \\
		& - Calculus \hfill Aug. 2019 \\
		& \\	
			
		% --- Section: Additional experience ---
		\nohyphens{\lefttitle{Additional}} 
		& {ARC Tokyo Japanese Language School} \hfill Tokyo, Japan \\
		\nohyphens{\lefttitle{Experience}}
		& Graduate School Preparation Class  \hfill Jul. 2017 – Mar. 2019\\
		& \\
				
		% --- Section: Academic Service ---		
		\nohyphens{\lefttitle{Academic Service}} 
		& Membership of \\
		& - The Operations Research Society of Japan \\
		& \\
						
		% --- Section: Various skills (programming, software, languages, etc.) ---		
		\nohyphens{\lefttitle{Computer Skills}} 
		& Matlab, Python, Latex, GuRoBi, Xpress.  \\
		&  \\
		
		\nohyphens{\lefttitle{Languages}} 
		& Chinese (Native), English (Fluent), Japanese (Fluent): JLPT N1.   \\
		&  \\



%		% --- Section: Other interests/hobbies ---
%		\nohyphens{\lefttitle{Other Interests}} 
%		& Some of your hobbies etc.  \\
		
		% --- End of CV! ---
		
	\end{longtable}
\end{document}
